Whole-body connectome of a segmented annelid larva

### 2024-10-25 Manuscript.qmd
ms update: add Suppl file desc
Suppl: change table 2 to csv, ms update
Ms: edits

Supplementary Table 1 lists all neuronal and non-neuronal cell types, their main annotations, including morphological, cell-class, segment, ganglion or sensory organ, neurotransmitter and neuropeptide phenotype, and main synaptic partners.
We also listed all literature references for previously published neuronal and non-neuronal cells and indicated which cells are reported here for the first time (105 cell types out of 294).
Interactive 3D morphological renderings of each cell type together with their main annotations can also be explored on a webpage (https://jekelylab.github.io/Platynereis_celltype_compendium.html and Supplementary file 1).
Querying by two or more annotations allows tallying the number of cells in different category (e.g. number of sensory cells with a single penetrating cilium or the number of gland cells in a particular segment)(Figure 3---figure supplement 3).

Left-right cell-type pairs have similar arbor morphologies (Figure 3---figure supplement 4).
The similar branching patterns for left and right cells of the same type is also indicated by their similar average Sholl diagrams (Figure 3---figure supplement 5).
Left-right pairs also have projections at symmetrical positions in the VNC indicating neuropil stereotypy (Figure 3---figure supplement 6).

@@

Supplementary file 1. 
A compressed (zip) stand-alone webpage listing all cell types together with their interactive 3D morphological rendering. After uncompressing the file, the Platynereis_celltype_compendium.html file can be opened in a browser.

>>>>

Supplementary Table 1 lists all neuronal and non-neuronal cell types, their main annotations, including morphological, cell-class, segment, ganglion or sensory organ, neurotransmitter and neuropeptide phenotype, and main synaptic partners.
We also listed all literature references for previously published neuronal and non-neuronal cells and indicated which cells are reported here for the first time (105 cell types out of 294).
Interactive 3D morphological renderings of each cell type together with their main annotations can also be explored on a webpage (https://jekelylab.github.io/Platynereis_connectome/celltype_compendium/index.html and Supplementary file 1).
Querying by two or more annotations allows tallying the number of cells in different category (e.g. number of sensory cells with a single penetrating cilium or the number of gland cells in a particular segment)(Figure 3---figure supplement 3).

Left-right cell-type pairs have similar arbour morphologies (Figure 3---figure supplement 4).
The similar branching patterns for left and right cells of the same type is also indicated by their similar average Sholl diagrams (Figure 3---figure supplement 5).
Left-right pairs also have projections at symmetrical positions in the VNC indicating neuropil stereotypy (Figure 3---figure supplement 6).

@@

Supplementary file 1. 
A compressed (zip) stand-alone webpage listing all cell types together with their interactive 3D morphological rendering. After uncompressing the file, the index.html file can be opened in a browser.
